---
title: "R Analysis"
author: "Jack Liu"
date: 2026-09-24
---
The Palmer Penguins dataset contains measurements of penguins from
three species collected in the Palmer Archipelago of Antarctica.

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/).
The data are available under a **CC0 (No Rights Reserved)** license.

## Looking at the data
First, I looked at the first few rows of the dataset to understand what variables are available.
```{r}
#| message: false
#| warning: false
library(palmerpenguins)
library(tidyverse)
penguins |>
  head()
```

## Number of penguins by species
Next, I counted the penguins by species
```{r}
species_counts <- penguins |>
  count(species, sort = TRUE)

species_counts
```

The results show that Adelie penguins have the most observations in the dataset, followed by Gentoo and Chinstrap penguins.

## Average body mass by species
Then, I looked into average body mass of penguins by species
```{r}
average_mass <- penguins |>
  group_by(species) |>
  summarise(average_body_mass = mean(body_mass_g, na.rm = TRUE)) |>
  arrange(desc(average_body_mass))

average_mass
```

Gentoo penguins have the highest average body mass, while Adelie penguins have the lowest average body mass.